Figures

### 2020-04-16 figures/07_model-selection.Rmd
avoid overlapping y-axis labels in re fig

```{r re, fig.width=4.25}
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0.3,0,0), "cm")), 
                   rel_widths = c(1, 0.8)),
cowplot::plot_grid(
  ggplot() + geom_blank() + theme(panel.background = element_blank()),
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")), 
rel_widths = c(0.15, 1)),
ncol = 1, rel_heights = c(1, 0.05))

>>>>

```{r re, fig.width=4.25}
cowplot::plot_grid(
  ggplot() + geom_blank() + theme(panel.background = element_blank()),
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.text.y = element_text(size = 9),
                                    axis.title.x = element_blank(), 
                                    plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0.3,0,0), "cm")), 
                   rel_widths = c(1, 0.8)),
cowplot::plot_grid(
  ggplot() + geom_blank() + theme(panel.background = element_blank()),
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")), 
rel_widths = c(0.15, 1)),
ncol = 1, rel_heights = c(1, 0.05)), 
ncol = 2, rel_widths = c(0.05, 1))
